### 2015-07-06 narrative/naming-service.tex
restructured naming and discovery to fit the standard pattern.

Given the well documented difficulties with POSIX-compliant naming and our
approach that decomposes what would be a single file into potentially large
number of objects, we must take a new approach to naming.  Data migration, as a
result of system pressures or user/system policies, further adds to the
complexity of managing naming and discovery. Our naming service must maintain
sufficient metadata information, track or be able to find objects as they move
across storage layers, and facilitates data discovery. Since we need to also
support access through POSIX APIs for existing application and system
integration, we must address how to bridge the drastic differences between the
decomposed objects of potentially varying fidelity with potentially multiple
version with a POSIX API-compatible interface.

Our research in this area will address the following questions:
(1) Since our metadata is distributed and partitioned, how do we respond to user
  requests within a specified time bound with accuracy? How do we estimate the
  completeness of the response?
(2) For POSIX API requests, how do we respond if only varying data fidelity levels
  are available for the requested data object?
(3) What level of metadata should we maintain and keep in sync to enhance response
  quality within time-bound requests?
(4) How much time should be allowed for searching for metadata given the user
  specified limits for data retrieval since the user will still have to spend
  the data retrieval time from different devices? How do we integrate the read
  time overhead into the metadata requests?
(5) How do we provide appropriate security while maintaining scalability,
  particularly with the distributed metadata stores?
% Which data block and what quality/type do we respond to a query with?;\\
% How will we scale a fully distributed storage system's metadata management;\\
% Can we accelerate the discovery process with the addition of an
%    application/user level metadata store that tracks where data was
%    originally written and how was it structured?;\\
% Can we provide time estimates for read/write calls in the presence of
%    an unbounded discovery system? If not how do we bound the discovery time?
% How do we amortize the time cost of discovery vs time cost of actually
%    reading the data (latency vs bandwidth essentially)?

@@

Our goal with this proposal is to offer a similar capability but with a finer
granularity leveraging the inner structure of scientific data. It must also
handle data discovery efficiently for cases where data is spread across several
storage layers or some of those pieces may have migrated based on system
pressures or user or system policies. Instead of a single file, such as might
be used to store an entire timestep output for a simulation, we will
demonstrate a metadata service with naming at the science variable level, but
with an associated list of all of the variable pieces and potentially different
versions stored throughout the storage system. By shifting to a finer-grained
approach, we will enable more effective use of close/fast/small storage tiers
and prioritize objects with high importance.  Traiditional HSM stores an entire
file on a tier making room if insufficient space is available.  With this shift
to a partial variable granularity, a 1 PB output with 500 GB of ``high
interest'' data can limit this costly tier usage to just 500 GB greatly
improving storage availability in the close/fast/small tier and focus
performance/capacity costs to get the most science from from the platform.  By
only placing ``high interest'' data in the close/fast/small tier, we will
effectively reduce pressure forcing data migration hurting both writing
performance and the later data analytics required for generating scientific
insights.  Sirocco identifies a data segment using a
contaier/object/fork/address tuple that can have associated attributes. We will
both add a special attribute indicating that this record is of ``high
interest'' as well adapting the migration mechanisms to use this attribute, if
present, to strongly encouraging keeping the record in close/fast/small storage
as long as possible.

@@

Structurally, the traditional POSIX naming service offeriing a hierarchical
space consisting of directories and files may be maintained for backwards
compatibility. However, this view will not offer the same strict semantics
POSIX defines. We must break these strict semantics to address scalability
problems forced by the serialized access to a single source for creating and
accessing files.  Several efforts~\cite{patil:2007:giga+,carns:pvfs} have worked to
reduce this contention by doing things like reducing the serialized scope to a
single directory or subtree or allowing a single process in a collective file
operation talk with the metadata service and distribute a handle to other
participants. While these approaches help, they do not address this key
scalability limitation of serialized access--even if the metadata service is
spread across multiple nodes. Instead, we will offer a short duration to
consistency POSIX view to offer the performance and consistency requirements an
exascale application demands.

We plan to address this scalability problem by continuing with the LWFS and
Sirocco model. LWFS and Sirocco have take an approach similar to the pure
object stores, but with a focus on the HPC setting. They have abandonded a
fully POSIX compliant metadata service as the default model in favor of a
container/object/fork/addrress tuple for identifying data similar to those used
for pure object stores. By having a service that addresses the object
collections that comprise a single thing, such as a variable or timestep
output, just enough metadata is maintained to make the storage system usable
without additional heavy lifting by clients.  LWFS demonstrated a POSIX-style
namespace on the side kept in sync using a transaction process like
D2T~\cite{lofstead:2012:txn} showing that this alternative approach can support traditional
POSIX API calls even though the underlying storage system uses a different
model. Because we are not requiring the entire storage space be addressible
from a single tree root, we can offer multiple independent roots using the
Sirocco object storage. We will investigate how to make the naming and
discovery service scalable under the circumstances outlined above.

@@

The main challenge of incorporating the additional, rich metadata will be
joined by the additional challenge of coordinating with the other storage and
application-layer services to offer the best access times possible for data
stored in the system. The developed metadata services that drive data
compression and subsetting operations must have easy, consistent, and ideally
non-blocking or locking access to this metadata service. We must investigate
how to build such a metadata and naming service that also incorporates and
maintains the additional metadata required to support our advanced
functionality.

>>>>

\paragraph{Background:}
Given the well documented difficulties with POSIX-compliant naming and our
approach that decomposes what would be a single file into potentially large
number of objects, we must take a new approach to naming.  Data migration, as a
result of system pressures or user/system policies, further adds to the
complexity of managing naming and discovery. Our naming service must maintain
sufficient metadata information, track or be able to find objects as they move
across storage layers, and facilitates data discovery. Since we need to also
support access through POSIX APIs for existing application and system
integration, we must address how to bridge the drastic differences between the
decomposed objects of potentially varying fidelity with potentially multiple
version with a POSIX API-compatible interface.

@@

@@

@@

\paragraph{Approach:}
Our goal with this proposal is to offer a similar capability but with a finer
granularity leveraging the inner structure of scientific data. It must also
handle data discovery efficiently for cases where data is spread across several
storage layers or some of those pieces may have migrated based on system
pressures or user or system policies. Instead of a single file, such as might
be used to store an entire timestep output for a simulation, we will
demonstrate a metadata service with naming at the science variable level, but
with an associated list of all of the variable pieces and potentially different
versions stored throughout the storage system. By shifting to a finer-grained
approach, we will enable more effective use of close/fast/small storage tiers
and prioritize objects with high importance.  Traiditional HSM stores an entire
file on a tier making room if insufficient space is available.  With this shift
to a partial variable granularity, a 1 PB output with 500 GB of ``high
interest'' data can limit this costly tier usage to just 500 GB greatly
improving storage availability in the close/fast/small tier and focus
performance/capacity costs to get the most science from from the platform.  By
only placing ``high interest'' data in the close/fast/small tier, we will
effectively reduce pressure forcing data migration hurting both writing
performance and the later data analytics required for generating scientific
insights.  Sirocco identifies a data segment using a
contaier/object/fork/address tuple that can have associated attributes. We will
both add a special attribute indicating that this record is of ``high
interest'' as well adapting the migration mechanisms to use this attribute, if
present, to strongly encouraging keeping the record in close/fast/small storage
as long as possible.

We plan to address scalability problems by continuing with the LWFS and Sirocco
model. LWFS and Sirocco have take an approach similar to the pure object
stores, but with a focus on the HPC setting. They have abandonded a fully POSIX
compliant metadata service as the default model in favor of a
container/object/fork/addrress tuple for identifying data similar to those used
for pure object stores. By having a service that addresses the object
collections that comprise a single thing, such as a variable or timestep
output, just enough metadata is maintained to make the storage system usable
without additional heavy lifting by clients.  LWFS demonstrated a POSIX-style
namespace on the side kept in sync using a transaction process like
D2T~\cite{lofstead:2012:txn} showing that this alternative approach can support
traditional POSIX API calls even though the underlying storage system uses a
different model. Because we are not requiring the entire storage space be
addressible from a single tree root, we can offer multiple independent roots
using the Sirocco object storage. We will investigate how to make the naming
and discovery service scalable under the circumstances outlined above.

\paragraph{Related Work:}
Structurally, the traditional POSIX naming service offeriing a hierarchical
space consisting of directories and files may be maintained for backwards
compatibility. However, this view will not offer the same strict semantics
POSIX defines. We must break these strict semantics to address scalability
problems forced by the serialized access to a single source for creating and
accessing files.  Several efforts~\cite{patil:2007:giga+,carns:pvfs} have
worked to reduce this contention by doing things like reducing the serialized
scope to a single directory or subtree or allowing a single process in a
collective file operation talk with the metadata service and distribute a
handle to other participants. While these approaches help, they do not address
this key scalability limitation of serialized access--even if the metadata
service is spread across multiple nodes. Instead, we will offer a short
duration to consistency POSIX view to offer the performance and consistency
requirements an exascale application demands.

\paragraph{Challenge:}
The main challenge of incorporating the additional, rich metadata will be
joined by the additional challenge of coordinating with the other storage and
application-layer services to offer the best access times possible for data
stored in the system. The developed metadata services that drive data
compression and subsetting operations must have easy, consistent, and ideally
non-blocking or locking access to this metadata service. We must investigate
how to build such a metadata and naming service that also incorporates and
maintains the additional metadata required to support our advanced
functionality.

Our research in this area will address the following questions:
(1) Since our metadata is distributed and partitioned, how do we respond to user
  requests within a specified time bound with accuracy? How do we estimate the
  completeness of the response?
(2) For POSIX API requests, how do we respond if only varying data fidelity
  levels are available for the requested data object?
(3) What level of metadata should we maintain and keep in sync to enhance
  response quality within time-bound requests?
(4) How much time should be allowed for searching for metadata given the user
  specified limits for data retrieval since the user will still have to spend
  the data retrieval time from different devices? How do we integrate the read
  time overhead into the metadata requests?
(5) How do we provide appropriate security while maintaining scalability,
  particularly with the distributed metadata stores?
